Stage 1 Registered Report: The error when inferring phylogenies with incipient species by a Birth-Death model

### 2018-04-04 article.tex
EOD

@@

@@

>>>>

This exploratorary research will produce a data set that maps the biological
parameters to the error made. The data set will consist out of two files:
one containing raw data, the other summarized data. 
A data file should be convenient to handle, thus as an upper limit for this data set's size, 
we use the maximum size of a table (called a data frame) of the R programming 
language. Within R, such a table may have maximally $2^{32}-1$ cells and occupy
less then 2 gigabytes in memory. 
The raw data file will contain parameters and 1000 nLTT statistics values.
Each row will contain the parameter set and these nLTT statistics.
From the constraints of the R programming language, this allows for 40K rows. 
The file with the summarized data will provide summary statistics of the raw
data. Each row will contain a parameter set, summary statistics and other
measurements. See the appendix, chapter 'Data set specifications', for the full list.

@@

[NOTE: as we know the expected number of lineages through time for both BD and PBD
model, we expect it to fall with the 95\% Highest Density Interval. It would also
increase support for Rampal's choice of parameter values (next to their 
computational feasability)]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data set specifications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The raw data file will consist of 40K rows. On each row there will be 1012 values:

\begin{itemize}  
  \item 12 simulation parameters:
  \begin{enumerate}  
    \item speciation initiation rate
    \item speciation completion rate
    \item extinction rate
    \item crown age
    \item crown age sigma
    \item sampling method
    \item mutation rate
    \item sequence length
    \item mcmc length
    \item tree sim rng seed
    \item alignment rng seed
    \item beast2 rnd seed
  \end{enumerate}
  \item 1000 nLTT statistics
\end{itemize}

The summarized data file will consist of 40K rows. On each row there will be 29 values:

\begin{itemize}  
  \item 12 simulation parameters:
  \begin{enumerate}  
    \item speciation initiation rate
    \item speciation completion rate
    \item extinction rate
    \item crown age
    \item crown age sigma
    \item sampling method
    \item mutation rate
    \item sequence length
    \item mcmc length
    \item tree sim rng seed
    \item alignment rng seed
    \item beast2 rnd seed
  \end{enumerate}
  \item number of taxa in incipient species tree (also: number of subspecies)
  \item number of taxa in species tree (also: number of species)
  \item mean nLTT statistic
  \item median nLTT statistic
  \item lower bound of 95\% HPD value of nLTT statistic
  \item upper bound of 95\% HPD value of nLTT statistic
  \item 11 ESSes of all parameters estimated by BEAST2:
  \begin{enumerate}  
    \item posterior
    \item likelihood 
    \item prior 
    \item treeLikelihood 
    \item TreeHeight 
    \item BirthDeath 
    \item BDBirthRate 
    \item BDDeathRate 
    \item logP.mrca 
    \item mrcatime 
    \item clockRate
  \end{enumerate}
\end{itemize}
